Focasting The Trend of Vehicle Related Crime In Calgary In 2025

### 2024-12-13 paper/paper.qmd
Revise the method for simulate data, correct some typo in paper

Urban crime is an ongoing problem compromising public confidence, economic stability, and safety[@un2012enhancing]. Among the several types of crimes, vehicle-related offenses include theft of vehicles and theft from vehicles remain a major issue in urban areas across the country[@rakauskas2009identification]. These crimes disturb people's life but also burden local governments and law enforcement. Over the years, Calgary, Canada, has seen varying patterns in vehicle-related crimes, which raises issues regarding future developments of these trends. Designing effective preventive plans, maximizing resource allocation, and guaranteeing community safety all depend on an awareness of current trends and future crime count prediction. This study forecasts vehicle-related crime patterns in Calgary up until 2025, therefore addressing these issues.

@@

```{r}
#| label: tbl-raw
#| tbl-cap: Column Names of Raw Data
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-combined-trend
#| fig-cap: Trend of The Two Crime Combined
#| echo: false
#| warning: false
# Plot combined trends
ggplot(cleaned_data, aes(x = time, y = crime_count, color = category)) +
  geom_line() +
  labs(
    title = "Trend of Theft FROM Vehicle and Theft OF Vehicle",
    x = "Time",
    y = "Crime Count",
    color = "Category"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
\newpage

@@

```{r}
#| label: fig-year-trend
#| tbl-cap: Trend of Crime Counts Over Years
#| echo: false
#| warning: false

ggplot(cleaned_data, aes(x = year, y = crime_count, color = category)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "Trend of Crime Counts Over Years",
    x = "Year",
    y = "Crime Count",
    color = "Category"
  ) +
  theme_minimal()

@@

```{r}
#| label: fig-forcast-trend
#| fig-cap: Actual vs. Fitted Crime Trends (2018-2025)
#| echo: false
#| warning: false
ggplot(fitted_data, aes(x = time, y = crime_count, color = category, linetype = source)) +
  geom_line() +
  labs(
    title = "Actual vs. Fitted Crime Trends (2018-2025)",
    x = "Time",
    y = "Crime Count",
    color = "Category",
    linetype = "Source"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

```{r}
#| label: fig-residual-plot
#| fig-cap: Residual Plot
#| echo: false
#| warning: false

>>>>

Urban crime is an ongoing problem compromising public confidence, economic stability, and safety[@un2012enhancing]. Among the several types of crimes, vehicle-related offenses include theft of vehicles and theft from vehicles remain a major issue in urban areas across the country[@rakauskas2009identification]. These crimes disturb people's life but also burden local governments and law enforcement[@crawford2009urban]. Over the years, Calgary, Canada, has seen varying patterns in vehicle-related crimes, which raises issues regarding future developments of these trends. Designing effective preventive plans, maximizing resource allocation, and guaranteeing community safety all depend on an awareness of current trends and future crime count prediction. This study forecasts vehicle-related crime patterns in Calgary up until 2025, therefore addressing these issues.

@@

```{r}
#| label: tbl-raw
#| tbl-cap: Column Names of Raw Data and first 6 rows of raw data
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-combined-trend
#| fig-cap: Monthly trend of Theft FROM Vehicle and Theft OF Vehicle
#| echo: false
#| warning: false
# Plot combined trends
ggplot(cleaned_data, aes(x = time, y = crime_count, color = category)) +
  geom_line() +
  labs(
    x = "Time",
    y = "Crime Count",
    color = "Category"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
\newpage

@@

```{r}
#| label: fig-year-trend
#| tbl-cap: Yearly trend of Theft FROM Vehicle and Theft OF Vehicle
#| echo: false
#| warning: false

ggplot(cleaned_data, aes(x = year, y = crime_count, color = category)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    x = "Year",
    y = "Crime Count",
    color = "Category"
  ) +
  theme_minimal()

@@

```{r}
#| label: fig-forcast-trend
#| fig-cap: Comparison of actual crime count of Theft OF Vehicle and Theft FROM Vehicle and Fitted value
#| echo: false
#| warning: false
ggplot(fitted_data, aes(x = time, y = crime_count, color = category, linetype = source)) +
  geom_line() +
  labs(
    x = "Time",
    y = "Crime Count",
    color = "Category",
    linetype = "Source"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

```{r}
#| label: fig-residual-plot
#| fig-cap: Residual again fitted plot
#| echo: false
#| warning: false
